Make any stupid plot you want

### 2020-12-03 draft/sections/math.tex
fleshing out locally trivial, making all disgrams equations so I can have references

When $E$ is a trivial fiber bundle $E = F \times K$, it can be assumed that all $F_{k}$ for $k \in K$ are equal. Fiber bundles are product spaces of toplological spaces, which are a set of points with a set of neighborhoods for each point\cite{some topology text book, really wikipedia}. We will be discussing total spaces $E$ that are locally trivial, meaning that for every point in K there exists an open set neighborhood $U$ such that if you restrict $E$ to that point, then  $\iota*E = F\times U$. [there's a missing sentance here...]

@@

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}. A fiber bundle is a structure $(E, K, \pi, F)$  consisting of topological spaces $E, K, F$ and the map from total space to base space $\pi: E \rightarrow K$.

\begin{tikzcd}
    F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                      & K \arrow[u, description, bend right]
\end{tikzcd}

By definition, every point in the base space $k \in K$ has a local neighborhood $U$ such that \pi()
\cite{rowlandFiberBundle,FiberBundle2020}

\begin{tikzcd}
    \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
    U                                                                         &                                         
\end{tikzcd}

There is a bijection from the fiber $F$ to the fiber $F_k$ over the point $k \in K$ such that 
\begin{equation}
\end{equation}

The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$. The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$

\begin{tikzcd}
    F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                      & K \arrow[u, "\sigma", description, bend right]
\end{tikzcd}

such that it is the right inverse of $\pi$:
\begin{equation}
    \pi(\sigma(k)) = k \text{ for all } \k \in K 
\end{equation}

In a locally trivial fiber bundle, $\sigma = K \times E$   \cite{weissteinFiberBundle}
\begin{equation}
\sigma(k) = (k, g(k))
\end{equation}

@@

\subsubsection{Base Space $K$}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}
%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary
%% k is a topological space ....equation soup

@@

@@

# C is more about naming types to reuse primatives

@@

\subsubsection{Subset}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U$ embedded in $K$ with the same fiber $\iota^*E$ and $\iota^*\sigma$.

\begin{tikzcd}
    \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
    U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
\end{tikzcd}

@@

and the sets correspond to the sections on $\S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber of $\mathbb{R}^7$ and a base space of $\S$:

\begin{tikzcd}
    \mathbb{R}^{7} \arrow[r, hook] & H \arrow[d, "\pi" description, bend right] \\
                                   & S \arrow[u, "\rho" description, bend right] 
\end{tikzcd}

@@

\subsubsection{Screen to Data}
%%diagram: [data] -Tau->[RGVXYZ]
%%%            \ /\ / 
\begin{tikzcd}
    E \arrow[d, "\pi" description] & H \arrow[d, "\pi" description]                                                 \\
    K \arrow[u, "\sigma" description, bend right] & S \arrow[l, "\xi" description] \arrow[u, "\rho" description, bend right]
\end{tikzcd}

The pullback $\xi$ on $S \rightarrow K$ means that the values in $E$ can be directly mapped to a simplex in $S$, which means there's a mapping from screen space back to the values.

\begin{tikzcd}
    \xi E \arrow[rr, "\tau" description] \arrow[rd, "\xi \sigma" description, bend right] &     & H \arrow[ld] \\
    & S \arrow[lu, bend right] &             
\end{tikzcd}

>>>>

When $E$ is a trivial fiber bundle $E = F \times K$, it can be assumed that all fibers $F_{k}$ over $k \in K$ are equal. Fiber bundles are product spaces of toplological spaces, which are a set of points with a set of neighborhoods for each point\cite{FiberBundle2020, rowlandFiberBundle}.

@@

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}. A fiber bundle is a structure $(E, K, \pi, F)$  consisting of topological spaces $E, K, F$ and the map from total space to base space:

\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                        & K \arrow[u, description, bend right]
    \end{tikzcd}
\end{equation}

where there is a bijection from $F$ to every fiber $F_k$ over point $k \in K$ in $E$ and the function $\pi: E \rightarrow K$ is the map into the $K$ quotient space of $E$.

Every point in the base space $k \in K$ has a local neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

\begin{equation}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                                         &                                         
    \end{tikzcd}
\end{equation}
$\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism such that $\pi$ and $\mathrm{proj}_U$ both map to $U$, the fiber over $k$ $F_k = \pi^{-1}({k \in K}) $ is homomorphic to the fiber $F$.  The base space $K$ carries the quotient topology determined by $\pi$, meaning it is

meaning that for every point $k in K$ there exists an open set neighborhood $U$ such that if $E$ is restricted to $k$ , then  $\iota*E = F\times U$. 
\begin{equation}
abc
\end{equation}

The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$. The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                        & K \arrow[u, "\sigma", description, bend right]
    \end{tikzcd}
\end{equation}

such that it is the right inverse of $\pi$:
\begin{equation}
    \pi(\sigma(k)) = k \text{ for all } k \in K 
\end{equation}

In a locally trivial fiber bundle, $\sigma = K \times E$ \cite{rowlandFiberBundle,FiberBundle2020}:
\begin{equation}
\sigma(k) = (k, g(k))
\end{equation}

@@

\subsubsection{Base Space $K$}

@@

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}
%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary
%% k is a topological space ....equation soup

@@

%% C is more about naming types to reuse primatives

@@

\subsubsection{Subset}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U$ embedded in $K$ with the same fiber $\iota^*E$ and $\iota^*\sigma$.   
\begin{equation}
    \begin{tikzcd}
        \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
        U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
    \end{tikzcd}    
\end{equation}

@@

and the sets correspond to the sections on $\S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber of $\mathbb{R}^7$ and a base space of $\S$:
\begin{equation}
    \begin{tikzcd}
        \mathbb{R}^{7} \arrow[r, hook] & H \arrow[d, "\pi" description, bend right] \\
                                    & S \arrow[u, "\rho" description, bend right] 
    \end{tikzcd}
\end{equation}

@@

\subsubsection{Screen to Data}
%%diagram: [data] -Tau->[RGVXYZ]
%%%            \ /\ / 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi" description] & H \arrow[d, "\pi" description]                                                 \\
        K \arrow[u, "\sigma" description, bend right] & S \arrow[l, "\xi" description] \arrow[u, "\rho" description, bend right]
    \end{tikzcd}
\end{equation}
The pullback $\xi$ on $S \rightarrow K$ means that the values in $E$ can be directly mapped to a simplex in $S$, which means there's a mapping from screen space back to the values. 
\begin{equation}
    \begin{tikzcd}
        \xi E \arrow[rr, "\tau" description] \arrow[rd, "\xi \sigma" description, bend right] &     & H \arrow[ld] \\
        & S \arrow[lu, bend right] &             
    \end{tikzcd}
\end{equation}
